```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ez)
#from https://github.com/cran/fifer/blob/master/R/chisqPostHoc.R
chisq.post.hoc <- function(tbl,test=c("fisher.test"), popsInRows=TRUE,control=c("fdr","BH","BY","bonferroni","holm","hochberg","hommel"),digits=4, ...) {
  #### extract correction method
  control <- match.arg(control)
  
  #### extract which test (fisher or chi square) 
  test = match.fun(test)

  #### test rows or columns
  if (!popsInRows) tbl <- t(tbl)
  popsNames <- rownames(tbl)
  
    #### come up with all possible comparisons
  prs <- combn(1:nrow(tbl),2)
  
  #### preallocate  
  tests <- ncol(prs)
  pvals <- numeric(tests)
  lbls <- character(tests)
  for (i in 1:tests) {
    pvals[i] <- test(tbl[prs[,i],], ...)$p.value
    lbls[i] <- paste(popsNames[prs[,i]],collapse=" vs. ")
  }
  adj.pvals <- p.adjust(pvals,method=control)
  cat("Adjusted p-values used the",control,"method.\n\n")
  data.frame(comparison=lbls,raw.p=round(pvals,digits),adj.p=round(adj.pvals,digits))
}

#from https://rdrr.io/cran/RVAideMemoire/src/R/se.R
se <-
function(x,y=NULL) {
  if (is.null(y)) {
    result <- sd(x,na.rm=TRUE)/sqrt(length(na.omit(x)))
  } else {
    p <- x/y
    result <- sqrt((p*(1-p))/y)
  }
  return(result)
}

print_ez_anova_result = function(ezANOVA_ret, df = F) {
  if (df) {
    cat(paste0('"(', ezANOVA_ret$ANOVA$DFn, ',', ezANOVA_ret$ANOVA$DFd, ')",'))
  }
  cat(ezANOVA_ret$ANOVA$F, ',',ezANOVA_ret$ANOVA$p, ',',ezANOVA_ret$ANOVA$ges, ',')
}

print_chi_square_result = function(res, df = F) {
  cat(res$statistic, ',',res$p.value,',')
}

my_ez_anova = function(mydata, mydv, mybetween) {
  #cat(!!!mydv, '\n')
  
  eval(parse(text=paste0("ezANOVA(mydata, dv=", mydv,", wid=ID, between=", mybetween, ", detailed=T)")))
  #print(ret)
}

do_anova = function(mydata, dv, between, show_df = F) {
  print_ez_anova_result(my_ez_anova(mydata, dv, between), df = show_df)
}

do_chi_square = function(mydata) {
  print_chi_square_result(chisq.test(mydata))
}

```


Statistics and Tests for Q1 to Q6 in Phase 2
======

# PA and PB

Answers of PA ("No" is correct):
```{r}
dat = read.csv('../survey-responses/responses.csv')
x = table(dat$PA.Answer)
x
```
Answers of PB ("Yes" is correct):
```{r}
x = table(dat$PB.Answer)
x
```

Both answers are correct:
```{r}
nrow(dat[dat$PB.Answer=='Yes'&dat$PA.Answer=='No', ])
```
# PC and PD

```{r echo=FALSE}
#erase C1_e to C1
dat[dat$Which.PC.=='C1_e',]$Which.PC. = 'C1'
dat$Which.PC. = factor(dat$Which.PC.)

dat[dat$Which.PD.=='D1_e',]$Which.PD. = 'D1'
dat$Which.PD. = factor(dat$Which.PD.)
```

## Q1: Error Token Highlighting
main effect of PC, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PC.Q1.rating", "Which.PC.")
```
```{r}
result$ANOVA$p
```
main effect of PD, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PD.Q1.rating", "Which.PD.")
```
```{r}
result$ANOVA$p
```
pairwise test for PC:
```{r}
pairwise.t.test(dat$PC.Q1.rating, dat$Which.PC., p.adjust = "bonferroni", pooled.sd=T)
```

pairwise test for PD:
```{r}
pairwise.t.test(dat$PD.Q1.rating, dat$Which.PD., p.adjust = "bonferroni", pooled.sd=T)
```

## Q2
main effect of PC, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PC.Q2..b..Please.rate.how.easy.or.how.difficult.it.is.to.figure.out.the.error.of.the.above.program.on.a.scale.from.1.to.10....1...means...very.easy....and...10...means...very.difficult....", "Which.PC.")
```
```{r}
result$ANOVA$p
```
main effect of PD, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PD.Q2..b..Please.rate.how.easy.or.how.difficult.it.is.to.figure.out.the.error.of.the.above.program.on.a.scale.from.1.to.10....1...means...very.easy....and...10...means...very.difficult....", "Which.PD.")
```
```{r}
result$ANOVA$p
```
pairwise test for PC:
```{r}
pairwise.t.test(dat$PC.Q2..b..Please.rate.how.easy.or.how.difficult.it.is.to.figure.out.the.error.of.the.above.program.on.a.scale.from.1.to.10....1...means...very.easy....and...10...means...very.difficult...., dat$Which.PC., p.adjust = "bonferroni", pooled.sd=T)
```

pairwise test for PD:
```{r}
pairwise.t.test(dat$PD.Q2..b..Please.rate.how.easy.or.how.difficult.it.is.to.figure.out.the.error.of.the.above.program.on.a.scale.from.1.to.10....1...means...very.easy....and...10...means...very.difficult...., dat$Which.PD., p.adjust = "bonferroni", pooled.sd=T)
```

## Q3
main effect of PC, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = chisq.test(table(dat[c("PC.Q3.rating", "Which.PC.")]))#my_ez_anova(dat, "PC.Q3.rating")
```
```{r}
result$p.value
```
main effect of PD, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = chisq.test(table(dat[c("PD.Q3.rating", "Which.PD.")]))#my_ez_anova(dat, "PC.Q3.rating")
```
```{r}
result$p.value
```
pairwise test for PC:
```{r}
tabs = xtabs(~Which.PC.+PC.Q3.rating, dat)
chisq.post.hoc(tabs,control=c("bonferroni"))
```

pairwise test for PD:
```{r}
tabs = xtabs(~Which.PD.+PD.Q3.rating, dat)
chisq.post.hoc(tabs,control=c("bonferroni"))
```

## Q4
main effect of PC, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PC.Q4..d..Given.the.above.error.messages..please.rate.how.easy.or.how.difficult.it.is.to.figure.out.the.error.of.the.above.program.on.a.scale.from.1.to.10..", "Which.PC.")
```
```{r}
result$ANOVA$p
```
main effect of PD, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PD.Q4..d..Given.the.above.error.messages..please.rate.how.easy.or.how.difficult.it.is.to.figure.out.the.error.of.the.above.program.on.a.scale.from.1.to.10..", "Which.PD.")
```
```{r}
result$ANOVA$p
```
pairwise test for PC:
```{r}
pairwise.t.test(dat$PC.Q4..d..Given.the.above.error.messages..please.rate.how.easy.or.how.difficult.it.is.to.figure.out.the.error.of.the.above.program.on.a.scale.from.1.to.10.., dat$Which.PC., p.adjust = "bonferroni", pooled.sd=T)
```

pairwise test for PD:
```{r}
pairwise.t.test(dat$PD.Q4..d..Given.the.above.error.messages..please.rate.how.easy.or.how.difficult.it.is.to.figure.out.the.error.of.the.above.program.on.a.scale.from.1.to.10.., dat$Which.PD., p.adjust = "bonferroni", pooled.sd=T)
```

## Q5
main effect of PC, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PC.Q5..e..Please.rate.the.helpfulness.of.the.above.error.messages.to.your.understanding.of.the.error.on.a.scale.from.1.to.10..", "Which.PC.")
```
```{r}
result$ANOVA$p
```
main effect of PD, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PD.Q5..e..Please.rate.the.helpfulness.of.the.above.error.messages.to.your.understanding.of.the.error.on.a.scale.from.1.to.10..", "Which.PD.")
```
```{r}
result$ANOVA$p
```
pairwise test for PC:
```{r}
pairwise.t.test(dat$PC.Q5..e..Please.rate.the.helpfulness.of.the.above.error.messages.to.your.understanding.of.the.error.on.a.scale.from.1.to.10.., dat$Which.PC., p.adjust = "bonferroni", pooled.sd=T)
```

pairwise test for PD:
```{r}
pairwise.t.test(dat$PD.Q5..e..Please.rate.the.helpfulness.of.the.above.error.messages.to.your.understanding.of.the.error.on.a.scale.from.1.to.10.., dat$Which.PD., p.adjust = "bonferroni", pooled.sd=T)
```

## Q6
main effect of PC, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
dat <- transform(dat, PC.Q6.rating = (PC.Q6.rating - min(PC.Q6.rating)) / (max(PC.Q6.rating) - min(PC.Q6.rating)))
                #dat = dat[dat$Q7.2=="No" & dat$Q301=="Yes",]
dat <- transform(dat, PD.Q6.rating = (PD.Q6.rating - min(PD.Q6.rating)) / (max(PD.Q6.rating) - min(PD.Q6.rating)))

result = my_ez_anova(dat, "PC.Q6.rating", "Which.PC.")
```
```{r}
result$ANOVA$p
```
main effect of PD, $p$-value:
```{r, echo=FALSE, warning=FALSE, results=FALSE, message=FALSE}
result = my_ez_anova(dat, "PD.Q6.rating", "Which.PD.")
```
```{r}
result$ANOVA$p
```
pairwise test for PC:
```{r}
pairwise.t.test(dat$PC.Q6.rating, dat$Which.PC., p.adjust = "bonferroni", pooled.sd=T)
```

pairwise test for PD:
```{r}
pairwise.t.test(dat$PD.Q6.rating, dat$Which.PD., p.adjust = "bonferroni", pooled.sd=T)
```
